A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-08 paper.tex
Edits to results table

The implementation of our algorithm uses \textsc{Glucose}~\cite{audemard2014}
for SAT solving and \textsc{Periplo}~\cite{rollini2013} for interpolant
generation. We intend to open source the tool for SYNTCOMP'16. The benchmarks
were run on a cluster of Intel Quad Core Xeon E5405 2GHz CPUs with 16GB of
memory.  The solver was allowed exclusive access to a node for one hour to
solve an instance.

The results of our benchmarking are shown, along with the synthesis competition
results~\cite{syntcompedacc}, in Table~\ref{tab:syntcomp}. The competition was
run on Intel Quad Core 3.2Ghz CPUs with 32GB of memory, also on isolated nodes
for one hour per instance. The unique column lists the number of instances that
only that tool could solve in the competition (excluding our solver). In
brackets is the number of instances that only that tool could solve, including
our solver.

\begin{table}
    \centering
    \setlength{\tabcolsep}{8pt}
    \begin{tabular}{l | r | r }
        \textbf{Solver} & \textbf{Solved} & \textbf{Unique} \\
        \hline
        Simple BDD Solver (2) & 195 & 10 \textit{(6)} \\
        AbsSynthe (seq2) & 187 & 2 \\
        Simple BDD Solver (1) & 185 & \\
        AbsSynthe (seq3) & 179 & \\
        Realizer (sequential) & 179 & \\
        AbsSynthe (seq1) & 173 & 1 \\
        Demiurge (D1real) & 139 & 5 \textit{(2)} \\
        Aisy & 98 & \\
        \textit{Unbounded Synthesis} & \textit{103} & \textit{12} \\
    \end{tabular}
    \caption{Synthesis Competition 2015 Results}
    \label{tab:syntcomp}
\end{table}

@@

We also present a cactus plot of the number of instances solved over time (Figure~\ref{fig:cactus}). For
reference we plotted our results along with \textsc{Demiurge}~\cite{bloem2014},
the only SAT-based tool in the competition, the winner of the sequential
realisability track \textsc{Simple BDD Solver 2}~\cite{walker2014}, and
AbsSynthe (seq3) \cite{brenguier2014}. Our results differ from the competition,
we suspect due to the weaker hardware.

@@

    \end{tikzpicture}
    \caption{Number of instances solver over time by the unbounded solver, Demiurge,
    and Simple BDD Solver.}\label{fig:cactus}
\end{figure}

>>>>

The implementation of our algorithm uses \textsc{Glucose}~\cite{audemard2014}
for SAT solving and \textsc{Periplo}~\cite{rollini2013} for interpolant
generation. We intend to open source the tool for SYNTCOMP'16. The benchmarks
were run on a cluster of Intel Quad Core Xeon E5405 2GHz CPUs with 16GB of
memory.  The solvers were allowed exclusive access to a node for one hour to
solve an instance.

The results of our benchmarking are shown, along with the synthesis competition
results~\cite{syntcompedacc}, in Table~\ref{tab:syntcomp}. The competition was
run on Intel Quad Core 3.2Ghz CPUs with 32GB of memory, also on isolated nodes
for one hour per instance. The competition results differ significantly from
our own benchmarks due to this more powerful hardware.  For our benchmarks we
report only the results for solvers we were able to run on our cluster. The
unique column lists the number of instances that only that tool could solve in
the competition (excluding our solver). In brackets is the number of instances
that only that tool could solve, including our solver.

\begin{table}
    \centering
    \setlength{\tabcolsep}{8pt}
    \begin{tabular}{l | r | r | r }
        \textbf{Solver} & \textbf{Solved} & \textbf{Solved} & \textbf{Unique} \\
                        & \textbf{(Competition)} & \textbf{(Benchmarks)} & \\
        \hline
        Simple BDD Solver (2) & 195 & 189 & 10 \textit{(6)} \\
        AbsSynthe (seq2) & 187 & 139 & 2 \\
        Simple BDD Solver (1) & 185 & 175 & \\
        AbsSynthe (seq3) & 179 & 134 & \\
        Realizer (sequential) & 179 & & \\
        AbsSynthe (seq1) & 173 & 139 & 1 \\
        Demiurge (D1real) & 139 & 136 & 5 \textit{(2)} \\
        Aisy & 98 & \\
        \textit{Unbounded Synthesis} & & \textit{103} & \textit{12} \\
    \end{tabular}
    \caption{Synthesis Competition 2015 Results}
    \label{tab:syntcomp}
\end{table}

@@

We also present a cactus plot of the number of instances solved over time
(Figure~\ref{fig:cactus}). We have plotted the best configuration of each
solver we benchmarked. The solvers shown are
\textsc{Demiurge}~\cite{bloem2014}, the only SAT-based tool in the competition,
the winner of the sequential realisability track \textsc{Simple BDD Solver
2}~\cite{walker2014}, and AbsSynthe (seq3) \cite{brenguier2014}.

@@

    \end{tikzpicture}
    \caption{Number of instances solved over time.}
    \label{fig:cactus}
\end{figure}
